Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law

### 2023-12-07 manuscript/manuscript.qmd
Add source links in case study

One key difference in these two organizations' differing registration strategies is their relationship with the government and alignment with government preferences. TNC has stated that its work "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others. [@ChinaPhilanthropyReserchInstitute:2018a] Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030). This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country. Moreover, TNC's work with local and national governments has generally been aligned with government preferences and directly benefits the regime.

In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo]. The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change", indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo]. In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo]. Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable. As a result, few potential PSUs have shown interest in sponsoring any potential registration attempt, and Greenpeace has chosen to not try to permanently register and instead work through repeated temporary activities.

>>>>

One key difference in these two organizations' differing registration strategies is their relationship with the government and alignment with government preferences. TNC has stated that its work "science-based" and that the organization uses a "non-confrontational, collaborative approach in working closely with governments, the business community and others. [@ChinaPhilanthropyReserchInstitute:2018a] Over its past two decades of work in China, TNC has provided technical support for the central government and local governments in Yunnan and Zhejiang Provinces, consulting on policies that have led to the establishment of national parks and nature reserves, and helping draft environmental policy proposals like the China National Biodiversity Conservation Strategy and Action Plan (2011–2030)[@todo]<https://www.nature.org/en-us/about-us/where-we-work/asia-pacific/china/stories-in-china/china-overview/>. This deliberately non-confrontational model, coupled with long-established partnerships with the government enabled TNC to secure the consent of a environment-focused national governmental agency to act as their PSU, which in turn allowed TNC to have a wider geographic reach throughout the country. Moreover, TNC's work with local and national governments has generally been aligned with government preferences and directly benefits the regime.

In contrast, Greenpeace engages in direct advocacy, "us[ing] peaceful protest and creative confrontation to expose global environmental problems" [@todo]<https://www.greenpeace.org/usa/about/>. The organization describes its work in China with phrases like "non-violent direct action," "impartiality and independence," and "brings change", indicating its dedication to maintaining organizational independence as it acts as an environmental watchdog [@todo]<https://www.greenpeace.org.cn/about/mission-and-value/>. In 2004, for instance, Greenpeace conducted three rounds of independent investigations into damages caused by the Sinar Mas Group, revealing how the Asian multinational corporation used promises of reforestation work as a cover while logging natural forests in Yunnan [@todo]<https://www.greenpeace.org.cn/2022/11/18/%e4%ba%a4%e9%94%8b%e4%ba%9a%e6%b4%b2%e6%9c%80%e5%a4%a7%e9%80%a0%e7%ba%b8%e5%b7%a8%e9%b3%84%ef%bc%8c%e5%ae%88%e6%8a%a4%e4%ba%91%e5%8d%97%e5%a4%a9%e7%84%b6%e6%9e%97-%e7%bb%bf%e8%89%b2%e5%92%8c/>. Greenpeace's ongoing independent advocacy work is often at odds with regime preferences, and from the government's perspective, its Chinese programming is unpredictable and less directly manageable. As a result, few potential PSUs have shown interest in sponsoring any potential registration attempt, and Greenpeace has chosen to not try to permanently register and instead work through repeated temporary activities.
